---
title: "Iteration and List Columns"
author: "Nidhi Patel"
date: "11/17/2020"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 6,
  out.width = "90%")

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_color_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Lists

You can put anything in a list

```{r}
l = list(
  vec_num = 5:8,
  vec_log = c(TRUE, TRUE, FALSE, TRUE, FALSE, FALSE),
  mat = matrix(1:8, nrow = 2, ncol = 4),
  summary = summary(rnorm(100))
)
#there is no way this would go into a dataframe (number of arguments do not match) but it can go into a list
```

How to access parts of list. 
```{r}
l$vec_num
l[[1]]
l[["vec_num"]]
```


## `for` loop

Create a new list

```{r}
list_norm = 
  list(
    a = rnorm(20, mean = 3, sd = 1),
    b = rnorm(30, mean = 0, sd = 5),
    c = rnorm(40, mean = 7, sd = .6),
    d = rnorm(50, mean = -3, sd = 1)
  )
```


```{r}
list_norm
```

Pause and get my old fn

```{r}
mean_sd = function(x) {
 if (!is.numeric(x)) {
   stop("Input must be numeric")
 }
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
  }
 mean_x = mean(x)
 sd_x = sd(x)
 
 tibble(
   mean = mean_x,
   sd = sd_x
 )
}
```

I can apply that fn to each list element

```{r}
mean_sd(list_norm[["a"]])
mean_sd(list_norm[["b"]])
mean_sd(list_norm[["c"]])
mean_sd(list_norm[["d"]])
```

Let's use a for loop:

```{r}
output = vector("list", length = 4)
#above is empty MAKE IT FIRST

for (i in 1:4) {
output[[i]] = mean_sd(list_norm[[i]])
}
#don't want to keep coyping over this line and change 1 to 2, 3, 4, etc. SO we use for loops
#use i as a placeholder

output
```

## Let's try a map

```{r}
map(list_norm, mean_sd)
# give it an input list and a fn i want to define. it gives the output a name

output = map(list_norm, mean_sd)
# output and map(sfsf) are the same thing.
```

What if you want a diff fn?

```{r}
output = map(list_norm, median)
```

```{r}
output = map_dbl(list_norm, median, .id = "input")
#map double gives me a vector 
```

```{r}
output = map_df(list_norm, mean_sd, .id = "input")
#can't make this a dbl bc the output are not individual number. 
#CAN make it a data frame
```

## List columns!
I want something to keep track of what output matches what input.


```{r}
listcol = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norm
  )
```

```{r}
listcol %>% pull(name)
listcol %>% pull(samp)
  

listcol %>% 
  filter(name == "a")
```


Let's try some operations

```{r}
listcol$samp #$ is the same as pulling

mean_sd(listcol$samp[[1]])
mean_sd(listcol$samp[[2]])
```

Can I jusp map??

```{r}
map(listcol$samp, mean_sd)
#now this is a list col inside a data frame, which we are mapping across lists 
```

So can I add a list column?? Yes!!!! mutate prob!!!

```{r}
listcol = listcol %>% 
  mutate(
    summary = map(samp, mean_sd), #don't need $ bc we're in mutate and piped
  medians = map_dbl(samp, median))
```

## Weather Data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors( 
    c("USW00094728", "USC00519397", "USS0023B17S"), 
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
    mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>% 
  select(name, id, everything())
```

Get our list columns..
```{r}
weather_nest = 
  weather_df %>%
  #nest: i want one df for cp, one for waikiki and one for waterhole
  nest(data = date:tmin)
```

```{r}
weather_nest %>% pull(name)
weather_nest %>% pull(data)

weather_nest$data[[1]]
```

Suppose U want to regress `tmax` and `tmin` for each station


```{r}
#THIS WORKS
lm(tmax ~ tmin, data = weather_nest$data[[1]]) #"~" is against tmax against (~) tmin
```

A function to do this regression
```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}
#weather_lm(weather_nest$data[[1]]) THIS FN CHECK WORKS
# I want the linear regression for all the data frames (HI and WA) too, so make a for loop

output = vector("list", 3)
for (i in 1:3) {
  output[[i]] = weather_lm(weather_nest$data[[i]])
}
```

What about map??

```{r}
map(weather_nest$data, weather_lm) #for each of the data tibbles, i want to apply my weather_lm fn 

```

What about a map in a list column??

```{r}
weather_nest %>% 
  mutate(models = map(data, weather_lm))
# we created a new list of the linear models.

#weather_nest$models #why does this not work??

```

