---
title: "Writing Functions"
author: "Nidhi Patel"
date: "11/16/2020"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 6,
  out.width = "90%")

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_color_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Do something simple

```{r}
x_vec = rnorm(30, mean = 5, sd = 3)

(x_vec - mean(x_vec)) / sd(x_vec)
#The above is the z-score
```
The summary numbers here show the z-scores. 

I want a function to compute z score

```{r}
  #everything that happens between these{} brackets is the body of my function.
#The input of the fn is x, we named it already
z_score = function(x) {
 
 z = (x - mean(x)) / sd(x)
  
  return(z)
  
}
# we named the z-score z, the return is z
z_score(x_vec)
```

Try my fn on some other things. These should giver errors

```{r, error = TRUE}
z_score(3)
#can compute the mean of 3, but cannot compute the sd, need more numbers to compute sd
z_score("my name is nidhi")
#can't do this either; cant take mean of character
z_score(mtcars)
#can't take the z-score of a data set
z_score(c(TRUE, TRUE, FALSE, TRUE))
#this works bc it is logical and coerces it to 0's and 1's.
#each of these is something that causes my fn to break. 

```

Update my fn

```{r}
z_score = function(x) {
 if (!is.numeric(x)) {
   stop("Input must be numeric")
 }
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
  }
 z = (x - mean(x)) / sd(x)
  
  return(z)
}

z_score(x_vec)
```

Try fn again, should also give errors

```{r, error = TRUE}
z_score(3)
z_score("my name is nidhi")
z_score(mtcars)
z_score(c(TRUE, TRUE, FALSE, TRUE))
#get input must be numeric!!!!!

```

## Multiple Outputs

```{r}
mean_sd = function(x) {
 if (!is.numeric(x)) {
   stop("Input must be numeric")
 }
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
  }
 mean_x = mean(x)
 sd_x = sd(x)
 
 tibble(
   mean = mean_x,
   sd = sd_x
 )
  
}
```

Check that fn works

```{r}
x_vec = rnorm(100, mean = 3, sd = 4)
mean_sd(x_vec)
```

Multiple inputs
I'd like to do this with a fn

```{r}
sim_data = 
  tibble(
    x = rnorm(100, mean = 3, sd = 4)
  )

sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )


```


```{r}
sim_mean_sd = function(samp_size, mu, sigma) {
  # mu = mean, sigma = sd
  sim_data = 
  tibble(
    x = rnorm(n = samp_size, mean = mu, sd = sigma)
  )

sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )
}

sim_mean_sd(100, 6, 3)
# having sim_mean_sd(samp_size = 100, mu = 6, sigma = 3) are NAME MATCHING
#here n =100, mu = 6 and sigma = 3. This creates a dataframe of this normal distribution following the mu and sigma of the sample size
```

```{r}
sim_mean_sd = function(samp_size, mu = 6, sigma = 3) {
  # the mu and sigma are defaulted here. When inputting sample size, we can override the default mu and sigma by specifiying mu = x and sigma = y
  sim_data = 
  tibble(
    x = rnorm(n = samp_size, mean = mu, sd = sigma)
  )

sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )
}

sim_mean_sd(100, mu = 4, sigma = 2) # this overrides the original mu and sigma inputs in the function
```

## Let's review Napopleon Dynamite

```{r}
napdyn_url = "https://www.amazon.com/Napoleon-Dynamite-Jon-Heder/product-reviews/B000I9U972/ref=cm_cr_getr_d_paging_btm_prev_1?ie=UTF8&reviewerType=all_reviews&pageNumber=1"

napoleon_html = read_html(napdyn_url)

review_titles = napoleon_html %>% 
  html_nodes(".a-text-bold span") %>% 
  html_text()

review_stars = napoleon_html %>% 
  html_nodes("#cm_cr-review_list .review-rating") %>% 
  html_text() %>% 
  str_extract("^\\d") %>% #this takes out the first digit
  as.numeric()

review_text = napoleon_html %>% 
  html_nodes(".review-text-content span") %>% 
  html_text() %>% 
  str_replace_all("\n", "") %>% #removes the \n at the beginning and end and replaces it with nothing
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

What about the next page of reviews?
I can copy and paste the code and change url to next page to get tibble of the next one.  Avoid this tediousness? Create a function!!!

```{r}

read_page_rev = function(url) {
    html = read_html(url)

review_titles = html %>% 
  html_nodes(".a-text-bold span") %>% 
  html_text()

review_stars = html %>% 
  html_nodes("#cm_cr-review_list .review-rating") %>% 
  html_text() %>% 
  str_extract("^\\d") %>% 
  as.numeric()

review_text = html %>% 
  html_nodes(".review-text-content span") %>% 
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)

reviews
}
```

Let's try out my function

```{r}
napdyn_url = "https://www.amazon.com/Napoleon-Dynamite-Jon-Heder/product-reviews/B000I9U972/ref=cm_cr_getr_d_paging_btm_prev_1?ie=UTF8&reviewerType=all_reviews&pageNumber=1"

read_page_rev(napdyn_url)
```

Let's read a few pages of reviews

With the function we can just change the url to every page and let it run the full fn

```{r}
napdyn_url_base = "https://www.amazon.com/Napoleon-Dynamite-Jon-Heder/product-reviews/B000I9U972/ref=cm_cr_getr_d_paging_btm_prev_1?ie=UTF8&reviewerType=all_reviews&pageNumber="

#url base is the url up to the page number

napdyn_urls = str_c(napdyn_url_base, 1:5)

napdyn_urls[1] #gives first page
napdyn_urls[3] #gives third page

more_reviews = bind_rows(
  read_page_rev(napdyn_urls[1]),
  read_page_rev(napdyn_urls[2]),
  read_page_rev(napdyn_urls[3]),
  read_page_rev(napdyn_urls[4]),
  read_page_rev(napdyn_urls[5])
)
#this part is still a little long lol. What if i wanted 30 pages?
```

## Mean scoping example

```{r}
f = function(x) {
  z = x + y
  z
}

x = 1
y = 2
#these x and y's are in the my global environment, not the fn
f(x = y)
# here it is saying x = y, so f(x = 2). Takes 2 and plugs into fn. Then the fn is saying it needs y, goes to global environment and finds it floating lol
# if there was "x1" in the fn, the fn would break bc there isn't a x1 in the global environment
```

## Fns as arguments

```{r}
my_summary = function(x, summ_func) {
  summ_func(x)
  
}

x_vec = rnorm(100, 3, 7)

mean(x_vec)
median(x_vec)

my_summary(x_vec, IQR)
```

